Job Demands-Resources Model Components through the Lens of O*NET Classifications

### 2023-03-04 Submission.tex
correlation table

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{O*Net, challenge-hindrance framework, job demands-resoures, job characteristics\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Job Demands-Resources Model Components through the Lens of O*NET Classifications},
  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resoures, job characteristics},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\abstract{%
Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demands. We build on a small but growing literature suggesting that individual differences may matter our perception of characteristics as demands and resources. The primary aims were to explore 1) whether there is variability in subjective ratings of job characteristics with respect to how much they served as resources and demands, and 2) whether or not there was a match between the literature-implicated resources/demands and subjective ratings of these characteristics. O*NET work characteristics were rated by 568 employed respondents in terms of relevance, perception as a demand, and perception as a resource. The results suggest that job characteristics differ in variability/stability regarding subjective worker perceptions, particularly for hindrance demands which showed the most variability. Job characteristics were not uniquely categorized as a resource or demand as evidenced by correlations, and lastly, literature-implicated resources not consistently rated as job resources or demands.
}

@@

In addition to highlighting extremely agreed- or disagreed-upon items, Figure \ref{fig:overallhist} presents our standard deviation indices across all rated items. Here, the Figure \ref{fig:combinegraphs} discrepancies recieve illumination, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram). Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. This points to \emph{hindrances}, in particular, as being likely amenable to future probing regarding moderating conditions. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} = 0.00 ). In sum, these results provide some collective support for H1, and particularly so for hindrances, which are consistently viewed as ``different''.

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table \ref{tab:cortab} provides the correlations among the O*Net item groupings by resource, challenge and hindrance demand. A large proportion of correlations are moderate. Challenge and hindrance demands are smaller in relationship, but mostly negative. Challenge and resource are strongly and positively related. These results provide support for H2 suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is percieved as a \emph{resource} being also percieved as a \emph{challenge}. Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.

@@

\small{

@@

1. onet.resource.ii & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
2. onet.resource.mp & .61*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.19 & 0.60\\
3. onet.resource.wo & .46*** & .50*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.79 & 0.84\\
4. onet.resource.io & .49*** & .64*** & .45*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.10 & 0.60\\
5. onet.resource.ir & .46*** & .55*** & .37*** & .60*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.80 & 0.61\\
6. onet.resource.pc & .19*** & .15*** & .32*** & .18*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.99 & 0.77\\
7. onet.resource.sc & .43*** & .46*** & .41*** & .45*** & .48*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.61\\
8. onet.challenge.ii & .62*** & .49*** & .37*** & .41*** & .33*** & .08 & .33*** & - &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
9. onet.challenge.mp & .47*** & .63*** & .42*** & .50*** & .41*** & .09* & .38*** & .65*** & - &  &  &  &  &  &  &  &  &  &  &  & 4.20 & 0.64\\
10. onet.challenge.wo & .34*** & .39*** & .64*** & .34*** & .30*** & .29*** & .38*** & .45*** & .49*** & - &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.88\\
11. onet.challenge.io & .34*** & .48*** & .33*** & .65*** & .48*** & .13** & .40*** & .50*** & .68*** & .43*** & - &  &  &  &  &  &  &  &  &  & 4.07 & 0.64\\
12. onet.challenge.ir & .32*** & .40*** & .26*** & .48*** & .63*** & .23*** & .39*** & .46*** & .60*** & .39*** & .70*** & - &  &  &  &  &  &  &  &  & 3.85 & 0.63\\
13. onet.challenge.pc & .12** & .08 & .21*** & .13** & .26*** & .66*** & .29*** & .14** & .12** & .33*** & .20*** & .31*** & - &  &  &  &  &  &  &  & 2.85 & 0.79\\
14. onet.challenge.sc & .27*** & .31*** & .28*** & .38*** & .40*** & .27*** & .62*** & .36*** & .41*** & .38*** & .51*** & .45*** & .40*** & - &  &  &  &  &  &  & 3.66 & 0.59\\
15. onet.hindrance.ii & -.26*** & -.26*** & -.17*** & -.24*** & -.18*** & -.02 & -.08 & -.27*** & -.26*** & -.10* & -.19*** & -.16*** & .06 & -.10* & - &  &  &  &  &  & 2.15 & 1.01\\
16. onet.hindrance.mp & -.23*** & -.30*** & -.17*** & -.22*** & -.15*** & .05 & -.07 & -.22*** & -.27*** & -.10* & -.18*** & -.15*** & .12** & -.06 & .86*** & - &  &  &  &  & 2.10 & 1.05\\
17. onet.hindrance.wo & -.21*** & -.25*** & -.22*** & -.22*** & -.06 & -.02 & -.12** & -.14** & -.21*** & -.23*** & -.15*** & -.09* & .05 & -.10* & .66*** & .69*** & - &  &  &  & 2.31 & 1.02\\
18. onet.hindrance.io & -.22*** & -.27*** & -.14*** & -.29*** & -.18*** & -.01 & -.10* & -.21*** & -.25*** & -.10* & -.27*** & -.19*** & .07 & -.10* & .79*** & .86*** & .69*** & - &  &  & 2.23 & 1.03\\
19. onet.hindrance.ir & -.22*** & -.24*** & -.15*** & -.24*** & -.25*** & -.06 & -.11** & -.19*** & -.21*** & -.08* & -.20*** & -.23*** & .04 & -.12** & .79*** & .80*** & .61*** & .82*** & - &  & 2.35 & 0.89\\
20. onet.hindrance.pc & -.04 & -.08* & -.09* & -.11** & -.10* & -.16*** & -.13** & -.03 & -.04 & -.06 & -.08* & -.10* & -.04 & -.13** & .38*** & .33*** & .47*** & .35*** & .47*** & - & 2.66 & 0.83\\
21. onet.hindrance.sc & -.13** & -.15*** & -.13** & -.19*** & -.13** & -.09* & -.23*** & -.12** & -.10* & -.05 & -.16*** & -.12** & -.01 & -.17*** & .62*** & .62*** & .56*** & .64*** & .66*** & .45*** & 2.64 & 0.80\\

@@

In addition to the two hypotheses, two related research questions were proposed. To answer these research questions, authors first categorized items into the JD-R elements listed in the JD-R literature. For example, autonomy is frequently described as a resource. An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?''. This O*Net item was therefore retained within the ``autonomy'' category. Means for resource, challenge, and hindrance groupings were then computed to explore whether literature-implicated resources and demands were evaluated as such. The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure). Here, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as ``high'' gray and black bars and ``low'' white bars). In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be ``hindrances'' at work. However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings. The white bars representing resources are consistently higher. In sum, these results provide some support for RQ 1 and 2.

Separate repeated-measures ANOVAs were conducted for each of these comparisons.

Repeated-measures ANOVAs were run for the group of literture-implicated demands first. The effect for \texttt{Overwork} was \(F_{(2, 1134)}\) = 17.71, partial eta squared \((\eta^2)\) was 0.03.
The effect for \texttt{Physical\ Environment} was \(F_{(2, 1108)}\) = 112.97 (\(\eta^2\) = 0.17).
The effect for \texttt{Time\ Pressure} was \(F_{(2, 1090)}\) = 82.22 (\(\eta^2\) = 0.13).
The effect for \texttt{Emotional\ Demands} was \(F_{(2, 1098)}\) = 393.43 (\(\eta^2\) = 0.42).
The effect for \texttt{Recipient\ Contact} was \(F_{(2, 1126)}\) = 1,031.73 (\(\eta^2\) = 0.65).
The effect for \texttt{Work\ Pressure} was \(F_{(2, 1132)}\) = 718.12 (\(\eta^2\) = 0.56).In all cases, statistical significance was less then .001, indicating in all cases, what the literature implicates is a demand was rated as a resource (all means are above the midpoint). See the patten of white resource bars on the lefthand side of Figure 4. This is contrary to the expectation that ratings would match our assumption of what a resource constitutes. Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.

Next, Repeated-measures ANOVAs were run for the group of literture-implicated resources (the right hand set of analyses presented in Figure 4). The effect for \texttt{Job\ Control} was \(F_{(2, 1134)}\) = 52.78 (\(\eta^2\) = 0.08).
The effect for \texttt{Participation} was \(F_{(2, 1124)}\) = 991.16 (\(\eta^2\) = 0.64).
The effect for \texttt{Autonomy} was \(F_{(2, 1074)}\) = 951.90 (\(\eta^2\) = 0.64).
The effect for \texttt{Team\ Cohesion} was \(F_{(2, 1120)}\) = 853.39 (\(\eta^2\) = 0.60).Similar to the demands analyses, statistical significance was less then .001 for all four category comparisons. Here, the pattern was as expected. Across categories, resources were rated the highest (see white bars representing resources in Figure 4).

@@

Theoretically, these findings support growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal. There is individual difference in how employees experience the characteristics of their jobs. Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand''.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Job Demands-Resources Model Components through the Lens of O*NET Classifications},
  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resoures, job characteristics},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{O*NET JD-R}
\keywords{O*Net, challenge-hindrance framework, job demands-resoures, job characteristics\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\abstract{
Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demands. We build on a small but growing literature suggesting that individual differences may matter our perception of characteristics as demands and resources. The primary aims were to explore 1) whether there is variability in subjective ratings of job characteristics with respect to how much they served as resources and demands, and 2) whether or not there was a match between the literature-implicated resources/demands and subjective ratings of these characteristics. O*NET work characteristics were rated by 568 employed respondents in terms of relevance, perception as a demand, and perception as a resource. The results suggest that job characteristics differ in variability/stability regarding subjective worker perceptions, particularly for hindrance demands which showed the most variability. Job characteristics were not uniquely categorized as a resource or demand as evidenced by correlations, and lastly, literature-implicated resources not consistently rated as job resources or demands.
}

@@

In addition to highlighting extremely agreed- or disagreed-upon items, Figure \ref{fig:overallhist} presents our standard deviation indices across all rated items. Here, the Figure \ref{fig:combinegraphs} discrepancies receive illumination, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram). Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. This points to \emph{hindrances}, in particular, as being likely amenable to future probing regarding moderating conditions. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} = 0.00 ). In sum, these results provide some collective support for H1, and particularly so for hindrances, which are consistently viewed as ``different.''

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table \ref{tab:cortab} provides the correlations among the O*Net item groupings by resource, challenge and hindrance demand. We would expect to see minimal correlations if job characteristics \emph{were} uniquely categorized. Here, we do expected to see more than minimal correlations. First, the mean correlation within resource categories was \_\_\_\_\_\_\_\_\_\_, \_\_\_\_\_\_\_\_\_ within challenge categories, and \_\_\_\_\_\_\_\_\_\_ within hindrance categories. We would expect these to be the highest. The mean resource to challenge correlation was \_\_\_\_\_\_\_\_\_\_. The mean resource to hindrance correlation was \_\_\_\_\_\_\_\_\_\_. Finally, the mean challenge to hindrance correlation was \_\_\_\_\_\_\_\_\_\_\_\_. These were expected to be moderate in size, but smaller than within the same category. In sum, Challenge and hindrance demands demonstrated smaller relationships, but mostly negative. Challenge and resource are strongly and positively related. These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a \emph{resource} being also perceived as a \emph{challenge}. Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.

@@

\tiny{

@@

1. onet.resource.ii & - & .61* & .46* & .49* & .46* & .19* & .43* & .62* & .47* & .34* & .34* & .32* & .12* & .27* & -.26* & -.23* & -.21* & -.22* & -.22* & -.04 & 3.98 & 0.80\\
2. onet.resource.mp &  & - & .50* & .64* & .55* & .15* & .46* & .49* & .63* & .39* & .48* & .40* & .08 & .31* & -.26* & -.30* & -.25* & -.27* & -.24* & -.08* & 4.19 & 0.60\\
3. onet.resource.wo &  &  & - & .45* & .37* & .32* & .41* & .37* & .42* & .64* & .33* & .26* & .21* & .28* & -.17* & -.17* & -.22* & -.14* & -.15* & -.09* & 3.79 & 0.84\\
4. onet.resource.io &  &  &  & - & .60* & .18* & .45* & .41* & .50* & .34* & .65* & .48* & .13* & .38* & -.24* & -.22* & -.22* & -.29* & -.24* & -.11* & 4.10 & 0.60\\
5. onet.resource.ir &  &  &  &  & - & .37* & .48* & .33* & .41* & .30* & .48* & .63* & .26* & .40* & -.18* & -.15* & -.06 & -.18* & -.25* & -.10* & 3.80 & 0.61\\
6. onet.resource.pc &  &  &  &  &  & - & .37* & .08 & .09* & .29* & .13* & .23* & .66* & .27* & -.02 & .05 & -.02 & -.01 & -.06 & -.16* & 2.99 & 0.77\\
7. onet.resource.sc &  &  &  &  &  &  & - & .33* & .38* & .38* & .40* & .39* & .29* & .62* & -.08 & -.07 & -.12* & -.10* & -.11* & -.13* & 3.65 & 0.61\\
8. onet.challenge.ii &  &  &  &  &  &  &  & - & .65* & .45* & .50* & .46* & .14* & .36* & -.27* & -.22* & -.14* & -.21* & -.19* & -.03 & 3.98 & 0.80\\
9. onet.challenge.mp &  &  &  &  &  &  &  &  & - & .49* & .68* & .60* & .12* & .41* & -.26* & -.27* & -.21* & -.25* & -.21* & -.04 & 4.20 & 0.64\\
10. onet.challenge.wo &  &  &  &  &  &  &  &  &  & - & .43* & .39* & .33* & .38* & -.10* & -.10* & -.23* & -.10* & -.08* & -.06 & 3.65 & 0.88\\
11. onet.challenge.io &  &  &  &  &  &  &  &  &  &  & - & .70* & .20* & .51* & -.19* & -.18* & -.15* & -.27* & -.20* & -.08* & 4.07 & 0.64\\
12. onet.challenge.ir &  &  &  &  &  &  &  &  &  &  &  & - & .31* & .45* & -.16* & -.15* & -.09* & -.19* & -.23* & -.10* & 3.85 & 0.63\\
13. onet.challenge.pc &  &  &  &  &  &  &  &  &  &  &  &  & - & .40* & .06 & .12* & .05 & .07 & .04 & -.04 & 2.85 & 0.79\\
14. onet.challenge.sc &  &  &  &  &  &  &  &  &  &  &  &  &  & - & -.10* & -.06 & -.10* & -.10* & -.12* & -.13* & 3.66 & 0.59\\
15. onet.hindrance.ii &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .86* & .66* & .79* & .79* & .38* & 2.15 & 1.01\\
16. onet.hindrance.mp &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .69* & .86* & .80* & .33* & 2.10 & 1.05\\
17. onet.hindrance.wo &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .69* & .61* & .47* & 2.31 & 1.02\\
18. onet.hindrance.io &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .82* & .35* & 2.23 & 1.03\\
19. onet.hindrance.ir &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .47* & 2.35 & 0.89\\
20. onet.hindrance.pc &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & 2.66 & 0.83\\
21. onet.hindrance.sc &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.64 & 0.80\\

@@

In addition to the two hypotheses, two related research questions were proposed: 1) do literature-implicated resources materialize as perceived resources and 2) do literature-implicated demands materialize as perceived demands? To answer these questions, authors first categorized O*Net items into the JD-R elements listed in the JD-R literature. For example, autonomy is frequently described as a resource in the JD-R literature. An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?'' This O*Net item was therefore retained within the ``autonomy'' category. Mean ratings of the O*Net items were then computed by element (e.g., all of the items representing autonomy) to explore whether literature-implicated resources and demands were evaluated as such.

Repeated-measures ANOVAs were computed for the group of literature-implicated \emph{resources} first (see the right hand side of Figure 4). The effect for \texttt{Job\ Control} was \(F_{(2, 1134)}\) = 52.78 (\(\eta^2\) = 0.08).
The effect for \texttt{Participation} was \(F_{(2, 1124)}\) = 991.16 (\(\eta^2\) = 0.64).
The effect for \texttt{Autonomy} was \(F_{(2, 1074)}\) = 951.90 (\(\eta^2\) = 0.64).
The effect for \texttt{Team\ Cohesion} was \(F_{(2, 1120)}\) = 853.39 (\(\eta^2\) = 0.60).Statistical significance was less then .001 for all four category comparisons. Here, the pattern was as expected. Across categories, resources were rated the highest (see white bars representing resources in Figure 4). However, as can be seen, mean challenge (which is a demand) was rated quite similarly and above the midpoint of 3 across JD-R categories.

Next, repeated-measures ANOVAs were then run for the group of literature-implicated \emph{demands}. See the left hand side of Figure 4. The effect for \texttt{Overwork} was \(F_{(2, 1134)}\) = 17.71, partial eta squared \((\eta^2)\) was 0.03. The effect for \texttt{Physical\ Environment} was \(F_{(2, 1108)}\) = 112.97 (\(\eta^2\) = 0.17). The effect for \texttt{Time\ Pressure} was \(F_{(2, 1090)}\) = 82.22 (\(\eta^2\) = 0.13). The effect for \texttt{Emotional\ Demands} was \(F_{(2, 1098)}\) = 393.43 (\(\eta^2\) = 0.42).
The effect for \texttt{Recipient\ Contact} was \(F_{(2, 1126)}\) = 1,031.73 (\(\eta^2\) = 0.65). The effect for \texttt{Work\ Pressure} was \(F_{(2, 1132)}\) = 718.12 (\(\eta^2\) = 0.56). In all cases, statistical significance was less then .001. However, the findings revealed that what the literature implicates as a demand was actually evaluated as a \emph{resource} (all resource means are above the midpoint). This is contrary to the expectation that ratings would match our assumption of what a demand constitutes. Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance. See the pattern of white resource bars on the left hand side of Figure 4.

Figure 4 presents these comparisons visually. First exploring the right side of Figure 4, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings. The white bars representing resources are consistently higher. As described above, the left side of Figure 4 shows literature-derived demand categories (e.g., work pressure). However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as ``high'' gray and black bars and ``low'' white bars). In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be ``hindrances'' at work. In sum, these results provide some support for RQ 1 and 2.

@@

Theoretically, these findings support growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal. There is individual difference in how employees experience the characteristics of their jobs. Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand.''
